TBD

### 2020-11-02 outputs/paper/paper.Rmd
4.04

The variables that we used in our dataset are as follow: 
-	age
     o	“What is your age”
     o	It provides an integer value greater than or equal to 18
-	education
     o	“What is the highest level of education you have completed?” 
     o	An extensive list of options are provided
-	Hispanic
     o	“Are you of Hispanic, Latino, or Spanish origin?” 
     o	An extensive list of options are provided 
-	household_income
     o	“What is your current annual household income before taxes? 
     o	Provides an extensive list of options beginning with $5,000 increments and then increases to $25,000 increments
     o	This is the variable in our dataset that many people did not feel comfortable answering and was left as N/A. When        cleaning the dataset, we removed all responses that left this answer as N/A  
-	race_ethnicity
     o	“What is your race”
     o	An extensive list of options are provided. 
-	extra_covid_worn_mask
     o	“Have you done any of the following in the past week? - Worn a mask when going out in public” 
     o	Yes or No options are available for the respondent to fill out 
-	state
     o	“Respondent’s state, as a two-character postal abbreviation. Calculated based on entered ZIP code.” 
     o	Manually filled out by respondent 
-	trump_biden
     o	“If the general election for president of the United States was a contest between Joe Biden and Donald Trump, who        would you support? “ 
     o	Options are either ‘Joe Biden’, ‘Donald Trump’, or ‘Don’t Know’

We also created another variable called ‘binary’ which outputs the result of the variable ‘trump_biden’ as a 1 or a 0 making it binary, therefore easier to analyze.

Key features of data?

>>>>

The variables that we used in our dataset are as follow: 
-	age
     o	“What is your age”
     o	It provides an integer value greater than or equal to 18
-	education
     o	“What is the highest level of education you have completed?” 
     o	An extensive list of options are provided
-	Hispanic
     o	“Are you of Hispanic, Latino, or Spanish origin?” 
     o	An extensive list of options are provided 
-	household_income
     o	“What is your current annual household income before taxes?" 
     o	Provides an extensive list of options beginning with $5,000 increments and then increases to $25,000 increments
     o	This is the variable in our dataset that many people did not feel comfortable answering and was left as N/A. When        cleaning the dataset, we removed all responses that left this answer as N/A  
-	race_ethnicity
     o	“What is your race”
     o	An extensive list of options are provided. 
-	extra_covid_worn_mask
     o	“Have you done any of the following in the past week? - Worn a mask when going out in public” 
     o	Yes or No options are available for the respondent to fill out 
-	state
     o	“Respondent’s state, as a two-character postal abbreviation. Calculated based on entered ZIP code.” 
     o	Manually filled out by respondent 
-	trump_biden
     o	“If the general election for president of the United States was a contest between Joe Biden and Donald Trump, who        would you support? “ 
     o	Options are either ‘Joe Biden’, ‘Donald Trump’, or ‘Don’t Know’

We also created another variable called ‘binary’ which outputs the result of the variable ‘trump_biden’ as a 1 or a 0 making it binary, therefore easier to analyze. [ADD INFORMATOIN ABOUT OTHER MUTATIONS WE CREATED]

```{r}
incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=15))
incomegraph
```

```{r}
raceinfo <- tbdata %>% group_by(race_ethnicity) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
racegraph <- raceinfo %>% ggplot(aes(x = "", y = prop, fill = race_ethnicity)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="What is your race?") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
     theme(text = element_text(size=13))
racegraph
```

```{r}
educationinfo <- tbdata %>% group_by(education_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
educationgraph <- educationinfo %>% ggplot(aes(x = "", y = prop, fill = education_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set2") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Education") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
     theme(text = element_text(size=15))
educationgraph
```

```{r}
ageinfo <- tbdata %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
agegraph <- ageinfo %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Age Groups") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4)+
     theme(text = element_text(size=13))
agegraph
```
Key features of data?
